\nopagenumbers
\headline={\centerline{$\oldstyle \folio \quad\cdotp\quad$Tom McCarthy}}
\def\paperwidth{144mm}
\def\paperheight{210mm}
\def\hmargin{20mm}
\def\tmargin{20mm}
\def\bmargin{20mm}
\special{papersize=\paperwidth, \paperheight}
\hsize=\paperwidth
\vsize=\paperheight
\hoffset=-1in
\voffset=-1in
\advance\hsize -\hmargin\relax
\advance\hsize -\hmargin\relax
\advance\vsize -\tmargin\relax
\advance\vsize -\bmargin\relax
\advance\hoffset \hmargin\relax
\advance\voffset \tmargin\relax

\newcount\chaptercount
\newcount\sectioncount
\font\chapterfont=cmb16
\def\chapter{
  \vfill\eject%
  \vglue 12mm
  \advance\chaptercount by 1
  \hfil {\chapterfont\the\chaptercount.} \hfil\par
  \sectioncount1\relax
}
\font\sectionfont=cmb14
\def\section{
  \vskip 12mm
  \parindent=0pt
  {\sectionfont\the\chaptercount.\the\sectioncount}
  \advance\sectioncount by 1
}

\chapter
\section
Turin is where the famous shroud is from, the one showing Christ's body supine after crucifixion: hands folded over genitals, eyes closed, head crowned with thorns.
The image isn't really visible on the bare linen.
It only emerged in the late nineteenth century when some amateur photographer looked at the negative of a shot he'd taken of the thing, and saw the figure---pale and faded, but there nonetheless.
Only in the negative: the nagative became a positive, which means that the shroud iself was, in effect, a negative already.
A few decades later, when the shroud was radiocarbon dated, it turned out to come from no later than the mid-thirteenth century; but this didn't trouble the believers.
Things like that never do.
People need foundation myths, some imprint of year zero, a bolt that secures the scaffolding that in turn holds fast the entire architecture of reality, of time: memory chambers and oblivion cellars, walls between eras, hallways that sweep us on towards the end-days and the coming whatever-it-is.
We see things shroudedly, as through a veil, an over-pixellated screen.
When the shapeless plasma takes on form and resolution, like a fish approaching us through murky waters or an image looming into view from noxious liquid in adarkroom, when it begins to coalesce into a figure that's discernible, if ciphered, we can say: {\it This is it, stirring, looming,} even if it isn't really, if it's all just ink-blots.

\section
One evening, a few years ago, I found myself stuck in Turin.
Not in the city, but the airport: Torino-Caselle.
Lots of other people did too: nothing was taking off.
The phrase {\it Await Announcements\/} multiplied, stacked up columns on the information screens, alternately in English and Italian.
What was causing the delay was a rogue aeroplane, some kind of private jet, which, ignoring all instructions, was flying in idiosyncratic patterns over Southern England and the Channel; which meant that no other planes could penetrate that swath of airspace; which in turn, via the series of switches and transfers and reroutings that had been put in place to deal with the whole situation, had spread a huge delay-cloud over Europe.
So I sat, like everyone else, sifting through airline- and airport-pages on my laptop for enlighthement about our quandry---then, when I'd exhausted these, clicking through news sites and social pages, meandering along corridors of trivia, generally killing time.

\section
That's when I read about the shroud.
When I'd done reading about that I started reading about hubs.
Torino-Caselle is a hub-airport.
There was a page on their website explaining what this is.
Hub-airports are predominantly transfer points, rather than destinations in and of themselves.
The website showed a diagram of a rimless wheel, with spokes of different lengths all leading to the centre, such that communication between any two spots on the wheels surface area was possible despite no direct line connecting these.
It looked like Jesus' crown, with all it's jutting prongs.
A link took me to an external page that explained how the hub-model was used in fields ranging from freight to distributed computing.
Soon I was reading about flanges, track sprockets and bearings in bicycle construction.
Then I clicked on {\it freehub}.
These incorporate splines---mating features for rotating elements---and a ratchet mechanism, built into the hub itself (rather than adjacent to or above it, as in previous, non-freehub models), whose temporary disengagement permits coasting.

\sectioncount11\relax
\section
I, for my part, stayed put, watching the crippled platform listing, the broken pipe gushing, the birds milling around, the oil-flower unfurling its petals, the dark water swellend and cresing, over and over again.
I watched, as I said, for hour after hour; when no public screen was showing these scenes, I watched them on first one and then another of my private ones.
They kept me utterly engrossed until, much later, in the small hours of the morning, the airspace unlocked and my flight was called.
Nor did I leave them behind me then.
When I had finally got airborne, I found my head slumped flat against the window as I slipped into a flecked and grainy sleep, oil seemed to lie around the very cloud-patches the wing-lights were illuminating: to lurk within and boost their volume, as though absorbed by them, and to seep out from them as well, in blobs and gobules that hovered on their ledges, sat about their folds and crevasses, like so many blackened cherubs.

\chapter
\section
Me?
Call me U.
It's not my intention, here, to write about the Koob-Sassen Project---to give and exegesis, overview, whatever, of it.
There are legal reasons for this: sub-clauses of contracts sitting in the drawers of cabinets that I always picture (and this, perhaps, it not unconnected to my sense of the Project itself, which I came to envision this way too) as made out of some smooth, post-metallic compound---epoxy, say, or Kevlar---although in reality they could just as well be aluminum, wooden, MDF or so on; stipulations protecting commercial, governmental and the level that comes one about that confidentiality; interdictions on virtually all types of disclosure.
ANd anyhow, even if there weren't, would you actually want to hear about it?

\bye%
